---
title: "Lab 00 - Hello IDS!"
author: "Alba Braham"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members .

```{r setup-tibble}
team_data <- tibble(
  name = c("Sophia", "Tarana", "May", 
           "Arshpreet", "Ada"),
  github_username = c("sophiacauter", "taranaedwards", "mayuco168", 
                      "arshpreet singh-04", "adaceylan04"), 
  colour = c("steelblue1", "purple4", "navy", 
             "blue", "red"),
  hobby = c("MathSoc netball", "journaling", "napping", 
            "reading", "crochet"),
  favourite_number = c(3, 4, 3, 7, 2 )
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


*This graph shows on the x axis, a GitHub username, and on the y axis, the height of each bar is the corresponding person's favourite number, with the colour of each bar being the person's favourite colour*

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "The Favourite Number and Colour of Each Member of the Group")
```

*The function labs() changes the axis and plot labels on a visualisation. After looking up using "??labs" the function labs() also modifies the legend of a visualisation*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*To display the data of everyone's hobby in the group/ in the whole course, it may be better to display each hobby as a segment of a pie chart. Or to display each hobby as a word, then increase the font size by 5 for each person >= 2 who also does that hobby, this would display both the number of different hobbies, while also demonstrating which hobbies are the most popular. Also I like this in italics (**)*
